---
title: "Healthcare Provider Comparison Tool Report"
author: ""
date: "`r paste0('Generated ', Sys.Date())`"
output: 
  pdf_document:
    latex_engine: pdflatex
    df_print: kable
params:
    state_selected: NULL
    county_selected: NULL
    group_one_bundle: NULL
    group_one_items: NULL
    group_two_items: NULL
    group_to_map: NULL
    var_to_map: NULL
    entity_types_included: NULL
    mean_provs_in_network_group_one_state: NULL
    mean_provs_in_network_group_one_county: NULL
    mean_provs_in_network_group_two_state: NULL
    mean_provs_in_network_group_two_county: NULL
    mean_provs_in_network_ratio_state: NULL
    mean_provs_in_network_ratio_county: NULL
    Map: NULL
header-includes:
  \usepackage{fancyhdr}
  \usepackage{helvet}
  \fancyhf{}
  \fancypagestyle{plain}{\pagestyle{fancy}}
  \pagestyle{fancy}
  \renewcommand{\familydefault}{\sfdefault}
  \fancyhead[R]{\thepage}
  \fancyfoot[C]{The Healthcare Provider Comparison Tool was created by Charm Economics, LLC in 2023.}
---


```{r include = F}
knitr::opts_chunk$set(echo = F, error = F, message = F)
library(kableExtra)
```

```{r renaming_params_to_shorter_names, include = F}
the_state = params$state_selected
the_county = params$county_selected
# the_loc = 'the United States'
#group_one_bundle = 'All Medical/Surgical'
group_one_items = stringr::str_replace_all(params$group_one_items,"<br>", "")
group_two_items = stringr::str_replace_all(params$group_two_items, "<br>", "")
group_to_map = params$group_to_map
var_to_map = params$var_to_map
# ent_types = params$entity_types_included
mean_g_one_state = as.numeric(params$mean_provs_in_network_group_one_state)
mean_g_one_county = as.numeric(params$mean_provs_in_network_group_one_county)
mean_g_two_state = as.numeric(params$mean_provs_in_network_group_two_state)
mean_g_two_county = as.numeric(params$mean_provs_in_network_group_two_county)
ratio_result_state = as.numeric(params$mean_provs_in_network_ratio_state)
ratio_result_county = as.numeric(params$mean_provs_in_network_ratio_county)
HHI = 'TBD'
leaflet_map = params$Map

```

```{r formatting_titles, include=F}
map_title = case_when(
  var_to_map == 'n' ~ 'Ratio of Number of Total Providers',
  var_to_map == 'people_per_provider' ~ 'Ratio of People per Provider',
  var_to_map == 'providers_per_pop_density_sq_mile' ~ 'Ratio of Providers / Population Density',
  var_to_map ==  'prop_in_bcbs' ~ 'Ratio of Percent of Providers in BCBS'
)

ratio_finding_levels = c('close to equal','moderately similar','moderately unequal','highly unequal')

ratio_finding = case_when(
  ratio_result_state <= 1.1 ~ ratio_finding_levels[1],
  ratio_result_state > 1.1 & ratio_result_state <= 2 ~ ratio_finding_levels[2],
  ratio_result_state > 2 & ratio_result_state <= 3 ~  ratio_finding_levels[3],
  ratio_result_state > 3 ~  ratio_finding_levels[4]
)

# ent_type_labels = case_when(
#   length(c(ent_types)) == 1 & ent_types == '1' ~ "Individual Providers (Individual NPIs only)",
#   length(c(ent_types)) == 1 & ent_types == '2' ~ "Organizational Providers (Organzation NPIs only)",
#   length(c(ent_types)) == 2 ~ 'Individual and Organizational Providers'
# )[1]

# ent_types[ent_types == "1"] <- “Individual Providers (Individual NPIs only)”
# ent_types[ent_types == "2"] <- “Provider Groups (Organizational NPIs only)”

```

```{r create_group_summaries, include= F}
  # Round numbers a bit for text. Maybe unnecessary.
  # digits_one_state = nchar(mean_g_one_state) - 3
  # digits_two_state = nchar(mean_g_two_state) - 3
  # 
  # den_one_state = 10^(digits_one_state)
  # den_two_state = 10^(digits_two_state)
#   
# if(var_to_map != 'prop_in_bcbs'){
#   summary_number_one_state = round(mean_g_one_state/den_one_state,3)*den_one_state
#   summary_number_two_state = round(mean_g_two_state/den_two_state,3)*den_two_state
# } else {
  summary_number_one_state = mean_g_one_state
  summary_number_two_state = mean_g_two_state
# }

# Group 1, State
summary_number_one_state_w_text = case_when(
  var_to_map == 'n' ~ as.character(summary_number_one_state),
  var_to_map == 'people_per_provider' ~ paste0(round(summary_number_one_state,1),' people per provider for '),
  var_to_map == 'providers_per_pop_density_sq_mile' ~ paste0('~',summary_number_one_state,' providers by population density for '),
  var_to_map == 'prop_in_bcbs' ~ paste0(100*mean_g_one_state,'% in network for ')
)

summary_number_one_state_w_text = paste0("There were ",summary_number_one_state_w_text," Medical/Surgical (Med/Surg) providers in ",ifelse(the_state == 'Contiguous USA', 'the Continental USA', the_state))

# Group 2, State

summary_number_two_state_w_text = case_when(
  var_to_map == 'n' ~ as.character(summary_number_two_state),
  var_to_map == 'people_per_provider' ~ paste0(round(summary_number_two_state,1),' people per provider for '),
  var_to_map == 'providers_per_pop_density_sq_mile' ~ paste0('~',summary_number_two_state,' providers by population density for '),
  var_to_map == 'prop_in_bcbs' ~ paste0(100*mean_g_two_state,'% in network for ')
)

summary_number_two_state_w_text = paste0(" and ",summary_number_two_state_w_text," Mental Health and Substance Use Disorder (MH/SUD) providers in ",ifelse(the_state == 'Contiguous USA', 'the Continental USA', the_state))

# Counties

# # Round numbers a bit for text. Maybe unnecessary.
# digits_one_county = nchar(mean_g_one_county) - 1
# digits_two_county = nchar(mean_g_two_county) - 1
# 
# den_one_county = 10^(digits_one_county)
# den_two_county = 10^(digits_two_county)

# if(var_to_map != 'prop_in_bcbs'){
#   summary_number_one_county = round(mean_g_one_county/den_one_county,1)*den_one_county
#   summary_number_two_county = round(mean_g_two_county/den_two_county,1)*den_two_county
# } else {
  summary_number_one_county = mean_g_one_county
  summary_number_two_county = mean_g_two_county
# }


# Group 1, county
summary_number_one_county_w_text = case_when(
  var_to_map == 'n' ~ as.character(summary_number_one_county),
  var_to_map == 'people_per_provider' ~ paste0(round(summary_number_one_county,1),' people per provider for '),
  var_to_map == 'providers_per_pop_density_sq_mile' ~ paste0('~',summary_number_one_county,' providers by population density for '),
  var_to_map == 'prop_in_bcbs' ~ paste0(100*mean_g_one_county,'% in network for ')
)

summary_number_one_county_w_text = paste0("There were ",summary_number_one_county_w_text," Medical/Surgical (Med/Surg) providers in ",ifelse(the_county == 'Contiguous USA', 'the Continental USA', the_county))

# Group 2, county

summary_number_two_county_w_text = case_when(
  var_to_map == 'n' ~ as.character(summary_number_two_county),
  var_to_map == 'people_per_provider' ~ paste0(round(summary_number_two_county,1),' people per provider for '),
  var_to_map == 'providers_per_pop_density_sq_mile' ~ paste0('~',summary_number_two_county,' providers by population density for '),
  var_to_map == 'prop_in_bcbs' ~ paste0(100*mean_g_two_county,'% in network for ')
)

summary_number_two_county_w_text = paste0(" and ",summary_number_two_county_w_text," Mental Health and Substance Use Disorder (MH/SUD) providers in ",ifelse(the_county == 'Contiguous USA', 'the Continental USA', the_county))
```

## Findings


- `r summary_number_one_state_w_text` `r summary_number_two_state_w_text`.
```{r add_in_county_summary_if_applicable, results = 'asis'}
if(the_county != 'All'){
  cat(paste0("- ",summary_number_one_county_w_text," ",summary_number_two_county_w_text,"."))
}
```
- The ratio of in-network Med/Surg providers to in-network MH/SUD providers at the `r ifelse(the_state != 'Contiguous USA', 'state', 'national')` level is `r round(ratio_result_state,2)`, which indicates that the proportion of providers in the two groups is `r ratio_finding`.

```{r summary_stats}
if(var_to_map != 'prop_in_bcbs'){
sum_stats = data.frame(
  Summary = c('Med/Surg Providers in Network',
              'MH/SUD Providers in Network',
              'Ratio of Med/Surg to MH/SUD in Network'),
  Value = c(
    as.character(round(summary_number_one_state,1)),
    as.character(round(summary_number_two_state,1)),
    as.character(ratio_result_state))
)
} else {
  sum_stats = data.frame(
  Summary = c('Med/Surg Providers in Network',
              'MH/SUD Providers in Network',
              'Ratio of Med/Surg to MH/SUD in Network'),
  Value = c(
    paste0(as.character(100*mean_g_one_county),'%'),
    paste0(as.character(100*mean_g_two_county),'%'),
    as.character(ratio_result_state))
)
}

if(the_state != 'Contiguous USA'){
  sum_stats = sum_stats |> 
    dplyr::rename(`State Summary` = Summary)
} else {
  sum_stats = sum_stats |> 
    dplyr::rename(`National Summary` = Summary)
}

knitr::kable(sum_stats,'pipe')
```
\begingroup
\fontfamily{phv}\fontsize{8}{10}\selectfont
*Note: For this ratio, a value of 1.5 or below was considered `r ratio_finding_levels[1]`, 1.5 - 2 was considered `r ratio_finding_levels[2]`, 2 - 2.5 was considered `r ratio_finding_levels[3]`, and anything greater than 2.5 was considered `r ratio_finding_levels[4]`.*
\endgroup


### `r map_title` in `r the_state`
```{r map, fig.align='center', out.width="80%"}
magick::image_read(params$Map) |>
  magick::image_resize('800x800')

# knitr::include_graphics(params$Map)
# library(leaflet)
# library(sf)
# 
# m = leaflet() |> 
#   addProviderTiles("CartoDB", 
#                    provider = providers$CartoDB) |> 
#   leaflet::setView(zoom = params$set_view$zoom,
#                    lat = params$set_view$lat,
#                    lng = params$set_view$lng) |> 
#   addPolygons(
#     label = ~state_name,
#     col = 'black',
#     weight = 2,
#     data = params$state_boundaries
#   ) |> 
#   addScaleBar('bottomright') |>
#   addPolygons(
#     group = 'mapped_polys',
#     color = 'black',
#     weight = 1,
#     fillColor = ~params$my_pal(var_chosen),
#     fillOpacity = 0.6,
#     opacity = 0.2,
#     label = ~ params$variable_label_ratio,
#     data = params$hsa_ratio
#   ) |>
#     addLegend(
#       pal = params$my_pal_legend,
#       title = params$legend_label,
#       na.label = '',
#       values = c(params$min_ratio,
#                  params$max_ratio)
#     )
# # Remove the zoom in/out buttons.
# m$x$options = append(m$x$options, list("zoomControl" = FALSE))
# 
# m
```

\begingroup
\fontfamily{phv}\fontsize{8}{10}\selectfont
*Note: Geographic units displayed in map are counties and states*
\endgroup

## Input Parameters

```{r inputs}
# Location Selected: `r the_loc`.
# Med/Surg Provider Types: `r group_one_items`.
# MH/SUD Provider Types: `r group_two_items`.
# Entity Types Included: `r ent_types`.

parameter_table = tibble(
    Input = c('State Selected',
              'Med/Surg Provider Types',
              'MH/SUD Provider Types'#,
              # 'Entity Types Included'),
    ),
    Value = c(the_state,
              paste0(group_one_items,collapse = ', '),
              paste0(group_two_items,collapse = ', ')#,
              # paste0(ent_type_labels,collapse = ", ")
    )
)

knitr::kable(parameter_table,'latex') |> 
  column_spec(1, width = "10em") |> 
  column_spec(2, width = "32em")
```

## Data Sources

Provider data was collected from the CMS National Plan and Provider Enumeration System (NPPES), which provides basic information about all organization and individual providers with a National Provider Identifier (NPI). This data was cross-referenced with a list of providers within the Blue Cross Blue Shield network provided by BCBS Minnesota. Providers are categorized according to the National Uniform Claim Committee (NUCC) Taxonomy classifications.  